Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-08-02 surfaces-write-up/surface-write-up.tex
respond to notation todo

Aaron: What does plural mean here?
I was thinking of doing something along the lines of
$R$ is generated in degree at most $g$ with relations in degree at most $r$. \\
Peter: The plural is signifying it is not just generated in 1 degree.  It is generated in all the degrees up to $g$ with relations generated in degrees all the degrees up to $r$.}

>>>>

Aaron: What does plural mean here?
I was thinking of doing something along the lines of
$R$ is generated in degree at most $g$ with relations in degree at most $r$. \\

Peter: The plural is signifying it is not just generated in 1 degree.  It is generated in all the degrees up to $g$ with relations generated in degrees all the degrees up to $r$. \\

Robin: Agree with Peter, because it's more accurate to say that the generators in $R$ lie in degrees $\leq r$.}
